Calculating the Solvent Exposed Surface Area of Proteins with Intersecting Spheres

### 2020-06-06 Paper.tex
Final Edits

\section{Supplemental Information}
List of PDB's used: \\
1W4H, 2FD7, 1I2U, 1HA8, 1RO3, 1FRE, 1AHL, 1B8W, 1B7I, 3UA6,\\
1B7K, 1IVA, 1L6H, 1KTH, 2GQV, 2KXK, 1CDT, 1BF0, 1B7V, 4AEI,\\
4BWS, 1UBQ, 1FGP, 1CPZ, 1B4R, 1CRE, 2BCB, 4ZK9, 1BCG, 1B3C,\\
1G47, 1NEI, 1HYM, 1A7H, 1COU, 4W9A, 1A70, 1EMV, 1AVS, 1QYS,\\
1BB8, 1HA6, 2HSH, 2ACY, 1THX, 2Z9H, 2CBM, 2APB, 2FLS, 1AIU,\\
4DZN, 1SRR, 2GZV, 2XKH, 1RKI, 1BMG, 2MCT, 1FI5, 1WOU, 1DZO,\\
1DC9, 5PC4, 1WDV, 2OXZ, 1P3B, 129L, 4FH1, 1S2B, 2R32, 1BWR,\\
6MKL, 3CS1, 3PMD, 2O35, 3S9B, 3PFC, 2CA8, 2EBY, 1IIB, 1GAJ,\\
1I9Q, 4LUP, 3RQ8, 1VHI, 5OIL, 6CW0, 2YM4, 2ZO1, 4KXO, 6G0M,\\
5R2D, 2GNP, 6F65, 2CM8, 5OH3, 2W5L, 2VV9, 6CQS, 6DJA, 6D40

Python Code:
\lstinputlisting[language=Python]{sasa.py}

>>>>

\section{Supplemental Information}
List of PDB's used: \\
1W4H, 2FD7, 1I2U, 1HA8, 1RO3, 1FRE, 1AHL, 1B8W, 1B7I, 3UA6,\\
1B7K, 1IVA, 1L6H, 1KTH, 2GQV, 2KXK, 1CDT, 1BF0, 1B7V, 4AEI,\\
4BWS, 1UBQ, 1FGP, 1CPZ, 1B4R, 1CRE, 2BCB, 4ZK9, 1BCG, 1B3C,\\
1G47, 1NEI, 1HYM, 1A7H, 1COU, 4W9A, 1A70, 1EMV, 1AVS, 1QYS,\\
1BB8, 1HA6, 2HSH, 2ACY, 1THX, 2Z9H, 2CBM, 2APB, 2FLS, 1AIU,\\
4DZN, 1SRR, 2GZV, 2XKH, 1RKI, 1BMG, 2MCT, 1FI5, 1WOU, 1DZO,\\
1DC9, 5PC4, 1WDV, 2OXZ, 1P3B, 129L, 4FH1, 1S2B, 2R32, 1BWR,\\
6MKL, 3CS1, 3PMD, 2O35, 3S9B, 3PFC, 2CA8, 2EBY, 1IIB, 1GAJ,\\
1I9Q, 4LUP, 3RQ8, 1VHI, 5OIL, 6CW0, 2YM4, 2ZO1, 4KXO, 6G0M,\\
5R2D, 2GNP, 6F65, 2CM8, 5OH3, 2W5L, 2VV9, 6CQS, 6DJA, 6D40.

PyRosetta Code:
\lstinputlisting[language=Python]{sasa.py}
